Cerebral malaria follow-up visit data

### 2021-08-19 cm_follow_up_figures.Rmd
updated follow-up analysis

# reorganize for plotting
df_results_all_plot <- df_results_all %>% 
  dplyr::filter(subject_id %in% df_fu_results$subject_id) %>% 
  pivot_longer(cols = 4:ncol(.), names_to = "variable", values_to = "value") %>% 
  mutate(follow_up = ifelse(grepl("fu", variable), "follow-up", "initial visit")) %>% 
  mutate(follow_up = factor(follow_up, levels = c("initial visit", "follow-up")))

@@

# THC
df_thc_compare <- df_results_all_plot %>% 
  dplyr::filter(variable %in% c("Hb_conc_overall_alpha", "Hb_conc_fu_alpha"))

@@

# O2 sat
df_o2sat_compare <- df_results_all_plot %>% 
  dplyr::filter(variable %in% c("Hb_o2sat_overall_alpha", "Hb_o2sat_fu_alpha"))

@@

@@

```{r fig5}

# plot O2 sat
df_results_all_plot %>% 
  dplyr::filter(!grepl("avg|second", variable)) %>% 
  mutate(measurement = ifelse(grepl("conc", variable), "THC", "O2_sat")) %>% 
  mutate(measurement = factor(measurement, levels = c("O2_sat", "THC"))) %>% 
  mutate(pvals = ifelse(measurement == "THC", round(thc_fu_pval, 3), round(o2sat_fu_pval, 3))) %>%

>>>>

# reorganize for plotting
df_results_all_plot <- df_results_all %>% 
  dplyr::select(-visit) %>% 
  dplyr::filter(subject_id %in% df_fu_results$subject_id) %>% 
  pivot_longer(cols = 4:ncol(.), names_to = "variable", values_to = "value") %>% 
  mutate(follow_up = ifelse(grepl("fu", variable), "follow-up", "initial visit")) %>% 
  mutate(follow_up = factor(follow_up, levels = c("initial visit", "follow-up")))

@@

  # averages

    # THC
    df_thc_compare <- df_results_all_plot %>% 
      dplyr::filter(variable %in% c("avg_Hb_conc", "avg_Hb_conc_fu"))

@@

    # O2 sat
    df_o2sat_compare <- df_results_all_plot %>% 
      dplyr::filter(variable %in% c("avg_Hb_o2sat", "avg_Hb_o2sat_fu"))

@@

  # alphas

    # THC
    df_thc_alpha_compare <- df_results_all_plot %>% 
      dplyr::filter(variable %in% c("Hb_conc_overall_alpha", "Hb_conc_fu_alpha"))

    thc_alpha_fu_pval <- wilcox.test(value ~ follow_up, data = df_thc_alpha_compare) %>% .$p.value

    # O2 sat
    df_o2sat_alpha_compare <- df_results_all_plot %>% 
      dplyr::filter(variable %in% c("Hb_o2sat_overall_alpha", "Hb_o2sat_fu_alpha"))

    o2sat_alpha_fu_pval <- wilcox.test(value ~ follow_up, data = df_o2sat_alpha_compare) %>% .$p.value

@@

#### A: Cerebral hemoglobin oxygen saturation & hemolgobin concentration
```{r fig5a}

df_results_all_plot %>%

  dplyr::filter(grepl("avg_Hb", variable)) %>% 
  mutate(measurement = ifelse(grepl("conc", variable), "THC", "O2_sat")) %>% 
  mutate(measurement = factor(measurement, levels = c("O2_sat", "THC"))) %>% 
  mutate(pvals = ifelse(measurement == "THC", round(thc_fu_pval, 3), round(o2sat_fu_pval, 3))) %>%

  facet_wrap(~measurement, scales = "free_y") +
  labs(y = "", x = "") +

#### B: Cerebral hemoglobin oxygen saturation & hemolgobin concentration alphas
```{r fig5b}

df_results_all_plot %>%

  dplyr::filter(!grepl("avg|second", variable)) %>% 
  mutate(measurement = ifelse(grepl("conc", variable), "THC", "O2_sat")) %>% 
  mutate(measurement = factor(measurement, levels = c("O2_sat", "THC"))) %>% 
  mutate(pvals = ifelse(measurement == "THC", round(thc_alpha_fu_pval, 3), round(o2sat_alpha_fu_pval, 3))) %>%
